Photo-D with LSST: stellar photometric distances out to the edge of the Galaxy

### 2024-09-01 paper/paper.tex
minor fixed in Sec. 4
Final edits to the TeX.

\author[0000-0001-5250-2633]{\v{Z}eljko Ivezi\'{c}}
\affiliation{Department of Astronomy and DiRAC Institute, University of Washington, Box 351580, Seattle, WA 98195, USA}

@@

\author[0009-0000-0990-8339]{Connor Yablonski}
\affiliation{Department of Astronomy, University of Washington, Box 351580, Seattle, WA 98195, USA}

@@

\author[ 	
0000-0003-3287-5250]{Neven Caplar}
\affiliation{Department of Astronomy and DiRAC Institute, University of Washington, Box 351580, Seattle, WA 98195, USA}

\author[0000-0003-1996-9252]{Mario Juri\'{c}}
\affiliation{Department of Astronomy and DiRAC Institute, University of Washington, Box 351580, Seattle, WA 98195, USA}

@@

\begin{acknowledgements}
This work is financed within the Tenure Track Pilot Programme of the Croatian Science Foundation and the Ecole Polytechnique Fédérale
de Lausanne and the Project TTP-2018-07-1171 ``Mining the Variable Sky'', with the funds of the Croatian-Swiss Research Programme. 
\v{Z}.I. acknowledges funding by the Fulbright Foundation and thanks the Ru\dj er Bo\v{s}kovi\'{c} Institute for hospitality. 
B.A. acknowledges helpful discussions with Douglas Tucker and the members of the Rubin Observatory Stack Club.

Funding for the SDSS and SDSS-II has been provided by the Alfred
P. Sloan Foundation, the Participating Institutions, the National
Science Foundation, the U.S. Department of Energy, the National
Aeronautics and Space Administration, the Japanese Monbukagakusho, the
Max Planck Society, and the Higher Education Funding Council for
England. The SDSS Web Site is \url{https://www.sdss.org/}.

>>>>

\author[0000-0001-5250-2633]{\v{Z}eljko Ivezi\'{c}}
\affiliation{DIRAC Institute and the Department of Astronomy, University of Washington, 3910 15th Avenue NE, Seattle, WA 98195, USA}

\author[0000-0003-3287-5250]{Neven \v{C}aplar}
\affiliation{DIRAC Institute and the Department of Astronomy, University of Washington, 3910 15th Avenue NE, Seattle, WA 98195, USA}

@@

\author[0009-0000-0990-8339]{Connor Yablonski}
\affiliation{DIRAC Institute and the Department of Astronomy, University of Washington, 3910 15th Avenue NE, Seattle, WA 98195, USA}

@@

\author[0000-0003-1996-9252]{Mario Juri\'{c}}
\affiliation{DIRAC Institute and the Department of Astronomy, University of Washington, 3910 15th Avenue NE, Seattle, WA 98195, USA}

@@

\begin{acknowledgements}
This work is financed within the Tenure Track Pilot Programme of the Croatian Science Foundation and the Ecole Polytechnique Fédérale
de Lausanne and the Project TTP-2018-07-1171 ``Mining the Variable Sky'', with the funds of the Croatian-Swiss Research Programme. 
Parts were based upon work supported by the National Science Foundation under Grant No. AST-2003196.

\v{Z}.I. acknowledges funding by the Fulbright Foundation and thanks the Ru{\dj}er Bo\v{s}kovi\'{c} Institute for hospitality. v{Z}.I, M.J. and N.\v{C}. acknowledge support from the DiRAC Institute in the Department of Astronomy at the University of Washington. B.A. acknowledges helpful discussions with Douglas Tucker and the members of the Rubin Observatory Stack Club.

The DiRAC Institute is supported through generous gifts from the Charles and
Lisa Simonyi Fund for Arts and Sciences and the Washington Research
Foundation. Funding for the SDSS and SDSS-II has been provided by the Alfred
P. Sloan Foundation, the Participating Institutions, the National
Science Foundation, the U.S. Department of Energy, the National
Aeronautics and Space Administration, the Japanese Monbukagakusho, the
Max Planck Society, and the Higher Education Funding Council for
England. The SDSS Web Site is \url{https://www.sdss.org/}.
